Embedding Dimension of Polyhedral Losses

### 2020-01-29 colt-20/embed-dim.tex
Added intro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
To do...

\subsection{Related works}
In the heuristic of \emph{empirical risk minimization}, the optimization of a loss function measuring error is canon in the design of machine learning algorithms designed for prediction tasks.
As the optimization of discrete problems is computationally hard, we typically resort to optimizing a \emph{surrogate loss} that yields desirable statistical guarantees such as the existence of excess risk bounds given by \emph{consistency}.

In particular,~\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.

In order to decrease the dimension of the optimization problem,~\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which is the minimum dimension input to a loss such that, for all beliefs $p$ over the outcomes, the ``correct report,'' a function of the distribution $p$, minimizes the expected loss over the distribution $p$.
In the more specific case on constructing \emph{convex, calibrated} surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
While~\cite{ramaswamy2016convex} present methods for obtaining lower bounds on convex calibration dimension for any discrete loss, their method does not always work well, as demonstrated by the $\abstain{\alpha}$ loss in Equation~\eqref{eq:abstain}.
\cite{ramaswamy2018consistent} present upper bounds on the convex calibration of $\abstain{\alpha}$ loss of $\ceil{\log_2(n)}$, but their characterization of lower bounds leave the tightness of these bounds as an open question.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
In empirical risk minimization, the optimization of a loss function measuring error is canon in the design of algorithms designed for prediction tasks.
For many categorical tasks (e.g. classification, ranking, top-$k$, set inclusion), one can often use their intuition to design a discrete loss that models the question they want to answer about their data.
For example, $0-1$ loss $\ell(r,y) = \Ind{r \neq y}$ gives punishment $1$ for a misprediction and $0$ for a correct prediction.
This problem naturally lines up with predicting the canonical classification problem.
Since the optimization of discrete problems is computationally hard, we typically resort to optimizing a \emph{surrogate loss} that yields desirable statistical guarantees such as the existence of excess risk bounds given by \emph{consistency}.
In the finite outcome setting, we know that calibration implies consistency, so we study the design of calibrated, convex losses-- specifically polyhedral (piecewise linear and convex) losses.

In this work, we propose a notion of measuring the efficiency of this specific class of calibrated surrogate losses, which~\cite{finocchiaro2019embedding} show are well-equipped to be surrogates for discrete losses.
Additionally, we present new techniques for finding lower bounds on this efficiency notion for a given discrete loss.

\subsection{Related works}
~\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.

In order to decrease the dimension of the optimization problem,~\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which is the minimum dimension input to a loss such that, for all beliefs $p$ over the outcomes, the ``correct report,'' a function of the distribution $p$, minimizes the expected loss over the distribution $p$.
In the more specific case on constructing \emph{convex} calibrated surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
While~\cite{ramaswamy2016convex} present methods for obtaining lower bounds on convex calibration dimension for any discrete loss, their method does not always work well, as demonstrated by the $\abstain{\alpha}$ loss in Equation~\eqref{eq:abstain}.
\cite{ramaswamy2018consistent} present upper bounds on the convex calibration of $\abstain{\alpha}$ loss of $\ceil{\log_2(n)}$, but their characterization of lower bounds leave the tightness of these bounds as an open question.
These upper bounds are, however, much tighter than the previous upper bounds of $(n-1)$ given by the different surrogates presented by~\cite{crammer2001algorithmic} and~\cite{rifkin2004defense}, and it is unclear what characteristics of the abstain loss allow us to exponentially reduce dimension of the input.
